### 2017-02-28 conclusion.tex
Added James' specific/easy comments

While a single galaxy can be a useful case study, multiple objects must be
studied in order to look at population-scale effects.  Chapter 4 extends the
results of chapter 3 by simulating an additional 17 objects, and uses these
simulations to examine if SN regulation can operate effectively in galaxies both
heavier and lighter than the Milky Way.  By creating a new sample of 18
simulated galaxies (the McMaster Unbiased Galaxy Simulations 2), we were able to
demonstrate a critical mass at which SN feedback breaks down as a regulator of
gas accretion and star formation.  Galaxies that exceed this mass, $(\sim
10^{12}\;\Msun)$, will produce more stars than real galaxies, and produce much
of these stars in a dense stellar bulge.  All of this arises due to a
fundamental relation between the mass loading of superbubble driven winds and
the mass of the galaxy (we found a relation between both disc and halo mass and
$\eta$).  When the escape velocity of the disc exceeds the sound speed of
superbubble-heated gas (which has a typical mass loading of $\eta=10$), only
outflows which have entrained less material are able to escape the galaxy,
leading to decreasing efficiency in ejecting material, and a shutdown of SN
regulation.  The fact that this shutdown occurs exactly where powerful AGN are
observed, and that it results in a vigorous transport of gas to the nucleus of
the galaxy make this result strong evidence that this shutdown acts as a 
``hand-off'' between SN and AGN feedback.

The MUGS2 simulations produced in chapter 4 contains a wealth of data
that is useful for future studies. Chapter 5 applied the MUGS2 sample of
galaxies we produced in \citet{Keller2016a} and used them to examine the radial
acceleration relation (RAR) that was derived by \citet{McGaugh2016} from
observations of the SPARC \citep{Lelli2016b} catalog.  Contrary to the assertions
of some \citep{Milgrom2016}, the tight relation seen in the SPARC data does not
require new fundamental physics (such as self-interacting dark matter, modified
gravity, or MOND).  Instead, the simple combination of dissipational collapse,
together with angular momentum conservation produces the RAR. This means that
even galaxies where SN fails to regulate their star formation (or even where SN
are omitted altogether) fall on the observed relation.  This was the first
published demonstration of this in simulation, using untuned simulations made
prior to the publication of \citet{McGaugh2016}.

@@

\section{The Impact and Context of these Results}
Developing a versatile, accurate, resolution insensitive model for SN feedback
has been a challenge in galaxy simulations for decades \citep{Katz1992}.  While
a number of recent models have been developed that are able to produce galaxies
which match some observables, all of these models have relied on purely
numerical features to enhance the effectiveness of feedback and counter the
losses due to limited resolution.  The \citet{Keller2014} model presented in
Chapter 2 is the first model of its kind that uses a first-principles approach
to prevent overcooling.  Beyond merely providing ``sufficient'' feedback, the
superbubble model also incorporates physics that previously have been omitted.
Thermal evaporation is a key process for mixing cold ISM with hot feedback
ejecta.  Prior to \citet{Keller2014}, this process was completely ignored, and
the local mass loading of feedback was set purely as a numerical parameter.
\citet{Rosdahl2016} illustrated this clearly, in a recent comparison project.
This paper implemented 5 popular feedback algorithms in the {\sc RAMSES} code:
simple thermal dumps; a delayed cooling model similar to \citet{Agertz2013}; a
kinetic model similar to \citet{DallaVecchia2008}; a stochastic thermal model
based on \citet{DallaVecchia2012}; and a hybrid model from \citet{Kimm2015}.
This allowed for a controlled test with isolated dwarf and Milky Way analog
galaxies. Each of these models, with ``fiducial'' parameter choices, produced
star formation rates that varied by nearly an order of magnitude in the
\citet{Kennicutt1998} star formation relation.  On top of that, the galaxies
showed marked morphological differences and average wind mass loadings that
varied by more than 4 orders of magnitude.  As we showed in \citet{Keller2015},
these winds are critical to the formation of galaxies like the Milky Way.  In
addition to the inter-model variation, \citet{Rosdahl2016} also found that the
numerical free parameters for each model had a vast impact on the resulting
galaxy's star formation rate, morphology, and outflow properties.  By building a
more conservative, physically motivated model where the local mass loading of
supernovae feedback is set by thermal evaporation, rather than numerically, we
can sidestep many of these issues.

Subgrid models are essential for including feedback from other mechanisms as
well.  Non-supernovae mechanisms for launching outflows and regulating star
formation are beginning to be studied with numerical simulations.  Radiation
pressure has been examined in a number of studies
\citep{Hopkins2014,Roskar2014,Agertz2015} using fairly simple treatments,
without full radiative transport.  These simulations have included various
models for feedback from SN and stellar winds, and have not produced consistent
conclusions as a result.  However, both \citet{Roskar2014} and
\citet{Agertz2015} found that the optical depths required for radiation pressure
to drive effective outflows produce unrealistic galaxy morphologies.  Cosmic
rays are beginning to be included in simulations with \citep{Girichidis2015} and
without \citep{Jubelgas2008,Booth2013} treatments for magnetohydrodynamics.
Most simulations have found that cosmic rays are unable to drive significant
outflows from Milky Way-like galaxies.  With a better constrained SN model,
these mechanisms can now be re-examined in the context of effective SN feedback.

@@

It has been suggested by numerous studies \citep{Benson2003,Bower2006} that AGN
feedback is critical to shaping the galaxy luminosity function.  Most
observations \citep{Kauffmann2003b} show that strong AGN are hosted in galaxies
with halo masses slightly greater than $\sim10^{12}\;M_\odot$.  By simulating a
collection of galaxies that bracket this mass, but omitting the effects of AGN
feedback, we were able to show that SN alone break down as a mechanism of
regulating star formation in these massive galaxies.  Importantly, this also
results in large angular momentum losses for gas within the disc, funneling
material to the central regions where SMBHs reside.  This, combined with the
failure of SN-driven galactic winds, suggests that SN are actually the mechanism
that sets where powerful AGN occur, a mechanism that has begun to be studied in
\citet{Bower2016}.

Chapter 5 presented the first simulation result to reproduce the
\citet{McGaugh2016} RAR.  A later study \citep{Ludlow2016} used data from the
EAGLE \citep{Schaye2015} and APOSTLE \citep{Sawala2016} simulations and
confirmed both the fit to the RAR, and the insensitivity to feedback that we
found.  Earlier, a semi-empirical model was used by \citet{DiCintio2016} showed
that a related observation, the mass-discrepancy acceleration relation, could be
produced simply as a result of other pre-existing scaling relations.  Taken
together, these results should seriously temper attempts to fit/explain the RAR
using new, exotic physics.  If conventional baryonic physics produces the same
relation in a $\Lambda CDM$ cosmology, there is little need to turn to modified
gravity \citep{Moffat2016,Verlinde2016} or new forces of nature
\citep{Burrage2016} to explain it.  Tests of cosmology have been moving closer
to scales where the effects of baryonic physics are becoming more pronounced.
Without well-constrained subgrid models, like the one presented here, we will be
unable to use the wealth of information available from galaxies to test new
theories of gravity or alternative cosmologies.  On individual galaxy scales,
$\Lambda CDM$ predictions {\it must} include the details of baryonic effects.
Chief among those effects is feedback.

@@

While observational evidence abounds for the existence of SMBHs
\citep{Kormendy2013}, and the impact of the AGNs they power
\citep{Veilleux2005}, there is still great uncertainty as to the details of how
they regulate their own growth, and the growth of the galaxies they live in.
\citet{Keller2016a} showed evidence that a transition occurs between galaxies
regulated by SN feedback to AGN feedback as they grow heavier than the Milky
Way.  How this handoff occurs remains widely unexplored.  The results presented
here provide a robust baseline for the effects of SN feedback, which is
necessary to constrain before adding additional physics to the simulations.
Using my superbubble feedback, along with new models for SMBH growth
\citep{Hopkins2010} and migration \citep{Tremmel2015}, we will be able to
simulate the growth of SMBHs in galaxies with greater confidence, using
physically motivated feedback and accretion models.  This will allow us to study
the full gamut of galaxies that exist, and study how the tight scaling relations
between stellar bulges and SMBHs might arise.

@@

While the MUGS2 sample has been simulated with a robust, physically motivated
model for SN feedback, its sample size is small (only 18 galaxies), and covers a
limited range of halo masses ($\sim 4\times10^{11}-2\times10^{12}\;M_\odot$).
Modern large volume simulations like Illustris \citep{Vogelsberger2014b} and
EAGLE \citep{Schaye2015} contain $>10^6$ individual galaxies, spanning a range
of masses that include both galaxies lighter and more massive than those we have
studied here.  These larger sample sizes are essential to understanding how
whole populations of galaxies evolved from the earliest linear structures.
While these simulations contain models for star formation, feedback from both
stars and AGN, as well as radiative cooling, these have all been fine-tuned to
fit observed scaling relations.  This limits the ability of these simulations to
explain the origins of the observations they have been tuned to fit.  My
superbubble model contains no free/tuned parameters, and accurately captures the
evolution of feedback-heated gas as it evaporates cool material that surrounds
it.  It is the only feedback model currently in existence that captures the
important physical process of thermal conduction and evaporation.  It will allow
us to build a statistically significant sample of physically realistic galaxies.
With first-principles, physically motivated models for the unresolved physics in
our simulations, we will be able to study the actual physics involved in shaping
both individual galaxies and the populations that we observe. 
\bibliographystyle{mnras}
\bibliography{library}

>>>>

While a single galaxy can be a useful case study, multiple objects must be
studied in order to look at population-scale effects.  Chapter 4 extends the
results of chapter 3 by simulating an additional 17 objects, and uses these
simulations to examine if SN regulation can operate effectively in galaxies both
heavier and lighter than the Milky Way.  By creating a new sample of 18
simulated galaxies (the McMaster Unbiased Galaxy Simulations 2), we were able to
demonstrate a critical mass at which SN feedback breaks down as a regulator of
gas accretion and star formation.  Galaxies that exceed this mass, $(\sim
10^{12}\Msun)$, will produce more stars than real galaxies, and produce much
of these stars in a dense stellar bulge.  All of this arises due to a
fundamental relation between the mass loading of superbubble driven winds and
the mass of the galaxy (we found a relation between both disc and halo mass and
$\eta$).  When the escape velocity of the disc exceeds the sound speed of
superbubble-heated gas (which has a typical mass loading of $\eta=10$), only
outflows which have entrained less material are able to escape the galaxy,
leading to decreasing efficiency in ejecting material, and a shutdown of 
regulation.  The fact that this shutdown occurs exactly as powerful AGN are
observed, and that it results in a vigorous transport of gas to the nucleus of
the galaxy make this result strong evidence that this shutdown acts as a 
``hand-off'' between SN and AGN feedback.

The MUGS2 simulations produced in chapter 4 contains a wealth of data that is
useful for future studies. Chapter 5 applied the MUGS2 sample of galaxies we
produced in \citet{Keller2016a} and used them to examine the radial acceleration
relation (RAR) that was derived by \citet{McGaugh2016} from observations of the
SPARC \citep{Lelli2016b} catalog.  The tight relation seen in the SPARC data
does not require new fundamental physics (such as self-interacting dark matter,
modified gravity, or MOND).  Instead, the simple combination of dissipational
collapse, together with angular momentum conservation produces the RAR. This
means that even galaxies where SN fails to regulate their star formation (or
even where SN are omitted altogether) fall on the observed relation.  This was
the first published demonstration of this in simulations, using untuned
simulations made prior to the publication of \citet{McGaugh2016}.

@@

\section{The Impact and Context of these Results}
Developing a versatile, accurate, resolution insensitive model for SN feedback
has been a challenge in galaxy simulations for decades \citep{Katz1992}.  While
a number of recent models have been developed that are able to produce galaxies
which match some observables, all of these models have relied on purely
numerical features to enhance the effectiveness of feedback and counter the
losses due to limited resolution.  The \citet{Keller2014} model presented in
Chapter 2 is the first model of its kind that uses a first-principles approach
to prevent overcooling.  Beyond merely providing ``sufficient'' feedback, the
superbubble model also incorporates physics that previously have been omitted.
Thermal evaporation is a key process for mixing cold ISM with hot feedback
ejecta.  Prior to \citet{Keller2014}, this process was completely ignored, and
the local mass loading of feedback was set purely as a numerical parameter.
\citet{Rosdahl2016} illustrated this clearly, in a recent comparison project.
This paper implemented 5 popular feedback algorithms in the {\sc RAMSES} code:
simple thermal dumps; a delayed cooling model similar to \citet{Agertz2013}; a
kinetic model similar to \citet{DallaVecchia2008}; a stochastic thermal model
based on \citet{DallaVecchia2012}; and a hybrid model from \citet{Kimm2015}.
This allowed for a controlled test with isolated dwarf and Milky Way analog
galaxies. Each of these models, with ``fiducial'' parameter choices, produced
star formation rates that varied by nearly an order of magnitude in the
\citet{Kennicutt1998} star formation relation.  On top of that, the galaxies
showed marked morphological differences and average wind mass loadings that
varied by more than 4 orders of magnitude.  As we showed in \citet{Keller2015},
these winds are critical to the formation of galaxies like the Milky Way.  In
addition to the inter-model variation, \citet{Rosdahl2016} also found that the
numerical free parameters for each model had a large impact on the resulting
galaxy's star formation rate, morphology, and outflow properties.  By building a
more conservative, physically motivated model where the local mass loading of
supernovae feedback is set by thermal evaporation, rather than numerically, we
can sidestep many of these issues.

Subgrid models are essential for including feedback from other mechanisms as
well.  Non-supernovae mechanisms for launching outflows and regulating star
formation are beginning to be studied with numerical simulations.  Radiation
pressure has been examined in a number of studies
\citep{Hopkins2014,Roskar2014,Agertz2015} using fairly simple treatments,
without full radiative transport.  These simulations have included various
models for feedback from SN and stellar winds, and have not produced consistent
conclusions as a result.  However, both \citet{Roskar2014} and
\citet{Agertz2015} found that the optical depths required for radiation pressure
to drive effective outflows produce unrealistic galaxy morphologies.  Cosmic
rays are beginning to be included in simulations with \citep{Girichidis2015} and
without \citep{Jubelgas2008,Booth2013} treatments for magnetohydrodynamics.
Most simulations have found that cosmic rays are unable to drive sufficiently
mass-loaded outflows from Milky Way-like galaxies.  With a better constrained SN
model, these mechanisms can now be re-examined with greater control, allowing SN
and other effects to be disentangled.

@@

It has been suggested by numerous studies \citep{Benson2003,Bower2006} that AGN
feedback is critical to shaping the galaxy luminosity function.  Most
observations \citep{Kauffmann2003b} show that strong AGN are hosted in galaxies
with halo masses slightly greater than $\sim10^{12}\;M_\odot$.  By simulating a
collection of galaxies that bracket this mass, but omitting the effects of AGN
feedback, we were able to show that SN alone break down as a mechanism of
regulating star formation in these massive galaxies.  Importantly, this also
results in large angular momentum losses for gas within the disc, funneling
material to the central regions where SMBHs reside.  This, combined with the
failure of SN-driven galactic winds, suggests that SN are actually the mechanism
that determines where powerful AGN occur, a mechanism that has begun to be studied in
\citet{Bower2016}.

Chapter 5 presented the first simulation result to reproduce the
\citet{McGaugh2016} RAR.  A later study \citep{Ludlow2016} used data from the
EAGLE \citep{Schaye2015} and APOSTLE \citep{Sawala2016} simulations and
confirmed both the fit to the RAR, and the insensitivity to feedback that we
found.  Earlier, a semi-empirical model was used by \citet{DiCintio2016} showed
that a related observation, the mass-discrepancy acceleration relation, could be
produced simply as a result of other pre-existing scaling relations.  Taken
together, these results should seriously temper attempts to fit/explain the RAR
using new, exotic physics.  If conventional baryonic physics produces the same
relation in a $\Lambda CDM$ cosmology, there is little need to turn to modified
gravity \citep{Moffat2016,Verlinde2016,Burrage2016} to explain it.  Tests of
cosmology have been moving closer to scales where the effects of baryonic
physics are becoming more pronounced.  Without well-constrained subgrid models,
like the one presented here, we will be unable to use the wealth of information
available from galaxies to test new theories of gravity or alternative
cosmologies, or constrain the effects of known physics: AGN, cosmic rays,
MHD effects, etc.  On individual galaxy scales, $\Lambda CDM$ predictions {\it must}
include the details of baryonic effects.  Chief among those effects is feedback.

@@

While observational evidence abounds for the existence of SMBHs
\citep{Kormendy2013}, and the impact of the AGNs they power
\citep{Veilleux2005}, there is still great uncertainty as to the details of how
they regulate their own growth, and the growth of the galaxies they live in.
\citet{Keller2016a} showed evidence that a transition occurs between galaxies
regulated by SN feedback to AGN feedback as they grow heavier than the Milky
Way.  How this handoff occurs remains widely unexplored.  The results presented
here provide a robust baseline for the effects of SN feedback, which is
necessary to constrain before adding additional physics to the simulations.
Using the superbubble feedback, along with new models for SMBH growth
\citep{Hopkins2010} and migration \citep{Tremmel2015}, we will be able to
simulate the growth of SMBHs in galaxies with greater confidence, using
physically motivated feedback and accretion models.  This will allow us to study
the full gamut of galaxies that exist, and study how the tight scaling relations
between stellar bulges and SMBHs might arise.

@@

While the MUGS2 sample has been simulated with a robust, physically motivated
model for SN feedback, its sample size is small (only 18 galaxies), and covers a
limited range of halo masses ($\sim 4\times10^{11}-2\times10^{12}\;M_\odot$).
Modern large volume simulations like Illustris \citep{Vogelsberger2014b} and
EAGLE \citep{Schaye2015} contain $>10^6$ individual galaxies, spanning a range
of masses that include both galaxies lighter and more massive than those we have
studied here.  These larger sample sizes are essential to understanding how
whole populations of galaxies evolved from the earliest linear structures.
While these simulations contain models for star formation, feedback from both
stars and AGN, as well as radiative cooling, these have all been fine-tuned to
fit observed scaling relations.  This limits the ability of these simulations to
explain the origins of the observations they have been tuned to fit.  The
superbubble model contains no free/tuned parameters, and accurately captures the
evolution of feedback-heated gas as it evaporates cool material that surrounds
it.  It is the only feedback model currently in existence that captures the
important physical process of thermal conduction and evaporation.  It will allow
us to build a statistically significant sample of physically realistic galaxies.
With first-principles, physically motivated models for the unresolved physics in
our simulations, we will be able to study the actual physics involved in shaping
both individual galaxies and the populations that we observe. 
\bibliographystyle{mnras}
\bibliography{library}
